%% Sometimes when a section can't be nicely modelled with the \entry[]... mechanism; hack our own
\makerubrichead{Employment}

\noindent\makefield{\faBookmark}{\textbf{Technique Expert (P7) in Secure Multiparty Computation group of Blockchain Department at Ant Financial (Alibaba Group)} \hfill Jul 2018 -- Apr 2019}\\
\smallskip
\setlength\parindent{18pt}\makefield{\faList}{Participate in desigining private query project of China Mobile.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Research and re-design existing Private Set Intersection scheme for China Mobile's project.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Participate in developing new Private Set Intersection scheme to support privacy-preserving intersection query on 100-million level dataset.}\\
\setlength\parindent{18pt}\makefield{\faList}{Participate in designing and developing privacy-preserving Logistic Regression model for over 20 finanacial institutions.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Design Secret Sharing scheme to protect the privacy of Logisitic Regression model.}\\		
\setlength\parindent{36pt}\makefield{\faChevronRight}{Enhance the existing model to support over 10,000 sample size and over 1000 feature size.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Develop the Garbled Circuit module to reduce modeling time by one magnitude.}\\
\setlength\parindent{18pt}\makefield{\faList}{Participate in designing and developing privacy-preserving GBDT model for over 20 finanacial institutions.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Research and design Garbled Circuit based scheme to protect the privacy of GBDT model.}\\		
\setlength\parindent{36pt}\makefield{\faChevronRight}{Independently research and develop core Garbled Circuit primitives.}\\	
\setlength\parindent{36pt}\makefield{\faChevronRight}{Design Garbled Circuit and Homomophic Encryption based privacy-preserving GBDT model.}\\
\setlength\parindent{18pt}\makefield{\faList}{Design the compiler for Secure Multiparty Computation.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Design the compiler to support both Garbled Circuit and Secret Sharing.}\\		
\setlength\parindent{36pt}\makefield{\faChevronRight}{Design the corresponding virtual machine to connect to the compiler.}\\	
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Software Engineer III in Trust and Identity Management team at Ebay Inc.} \hfill May 2016 -- Jul 2018}\\
\smallskip
\setlength\parindent{18pt}\makefield{\faList}{Design and develop push notification based multi-factor authentication.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Develop the push notification multi-factor authentication and integrate to Ebay FIDO server.}\\
\setlength\parindent{18pt}\makefield{\faList}{Participate in developing Single Sign On support for password-less access to Ebay.}\\
\setlength\parindent{18pt}\makefield{\faStar}{Participate in designing and developing RESTful services to migrate existing sign-in system for better system isolation.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Research on existing sign-in system services based on different user types and service types.}\\
\setlength\parindent{36pt}\makefield{\faChevronRight}{Developing Cookie library for different type of users.}\\
\setlength\parindent{18pt}\makefield{\faList}{Developing commercial RESTful serivce to track user sign-in activities for data analysis.}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Software Engineer Internship at Nok Nok Labs.} \hfill Jan 2015 -- Dec 2015}\\
\smallskip
\makefield{\faList}{Designed and implemented multi-factor authentication functionality with IBM Tivoli Server.}\\
\makefield{\faList}{Implemented and productized a multi-tenant access control and multi-factor authentication system.}\\
\makefield{\faList}{Developed a bootstrap web application for multi-factor authentication system to bootstrap an end-user with email registration.}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Head Teaching Assistant at Com S Department, Iowa State University.} \hfill Sep 2013 -- Dec 2014}\\
\smallskip
\makefield{\faList}{COM S 106: Introduction to Web Programming (Instructor: Dr. Susan (Shu-Hui) Chang)}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Teaching Assistant at Com S Department, Iowa State University.} \hfill Jan 2012 -- Sep 2013}\\
\smallskip
\makefield{\faList}{COM S 103: Computer Applications (Instructor: Dr. Susan (Shu-Hui) Chang)}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Teaching Assistant at Com S Department, Iowa State University.} \hfill Jan 2012 -- May 2012}\\
\smallskip
\makefield{\faList}{COM S 552: Principles of Operating Systems (Instructor: Dr. Wensheng Zhang)}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Research Assistant at Com S Department, Iowa State University.} \hfill Sep 2010 -- Dec 2011}\\
\smallskip
\makefield{\faList}{I worked with Dr. Wensheng Zhang (Com S Department) and Dr. Daji Qiao (ECE Department) from Iowa State University. My research interests are applied cryptography and computer security/privacy, including but not only restricted to security and privacy system and algorithm designs in systems, databases, networking.}\\
\smallskip

\noindent\makefield{\faBookmark}{\textbf{Research Internship at State Key Laboratory of Information Security, Chinese Academy of Sciences.} \hfill Jun 2009 -- Aug 2009}\\
\smallskip
\makefield{\faList}{I worked with Dr. Yuqing Zhang on summer intern project ``Research on the Impact of RepTrap Attack to Trust Management System''.}\\
\setlength\parindent{0pt}